Coupling microsimulation models with land-use transport models

### 2019-02-05 main.tex
Update on Overleaf.

%%%%%%%%%%%%
\section{Scientific landscape}

@@

@@

@@

@@

%%%%%%%%%%%%
\begin{table}
\begin{threeparttable}
	\caption{Main characteristics of QUANT and MOSES models.}\label{tab:comparison}
	\centering
	\begin{tabular}{|c|p{6cm}|p{6cm}|}
	\toprule
	& QUANT & MOSES \\
	\midrule
Time scale & 10 years $^{\ast 1}$ & 30 years \\
Spatial scale & UK & UK \\
Spatial resolution & Ward & Ward \\
Agent granularity & Aggregated counts & Person level \\
Static/Dynamic & Equilibrium (static) & Dynamic $^{\ast 2}$ \\
Randomness & Deterministic & Monte-Carlo simulations \\
Process: Transportation & 3 modes $^{\ast 3}$ & NA \\
Process: Economic activities & Accessibility-based relocations & NA \\
Process: Demographics & NA & Data-driven $^{\ast 4}$ \\
Process: Migration flows & Accessibility-based relocations & Data-driven \\
\bottomrule
	\end{tabular}
	\begin{tablenotes}
      \small
      \item $^{\ast 1}$ stylized time scale of metropolitan relocations \cite{wegener2004land}
      \item $^{\ast 2}$ model structure is however stationary - this is an important issue for a possible application to 2070
      \item $^{\ast 3}$ discrete choice for transportation mode is not implemented in QUANT \textbf{(?)} 
      \item $^{\ast 4}$ probabilities of basic demographic events (ageing, mortality, fertility, household formation, health, migration) are computed from data
    \end{tablenotes}
	\end{threeparttable}
\end{table}
%%%%%%%%%%%%

@@

\begin{itemize}
	\item Matsim is an agent-based approach to transportation demand which is activity-based \cite{horni2016multi}. It can simulate agents behavior within the transportation system (traffic flows) and behavioral patterns generating the travel demand. According to \cite{wise2016transportation}, accurate description of transportation remains a point to be explored for agent-based model. A weak coupling of Quant and Matsim would be interesting in that sense, and allow to precisely explore the consequence of transportation scenarios.
	\item More generally, the fuzzy boundary between microsimulation and agent-based modeling may be an interesting point to be investigated, both methodologically and theoretically.
\end{itemize}

>>>>

\subsection{Microsimulation models}

\cite{orcutt1957new} introduced the seminal idea of dealing with individual units which led to the emergence of microsimulation approaches in for socio-economic systems.

\cite{birkin2012review} review :
\begin{itemize}
    \item Privileged fields of application for policy evaluation: taxation scheme evaluation; pension management anticipation; health (environment-dependant conditions and spatial distribution of health services); transport (traffic microsimulations - \textit{even closer to ABMs in this field, the difference would be the application to policies or network interventions, rather than a principal focus on agent behavior}).
    \item Static vs Dynamic: static has fixed rules and updates weights e.g, dynamic simulates interactions and endogenous changes; static is cheap computationally.
    \item Spatial aspect: inclusion of precise local context; various sources and application to projections.
    \item Need for new hybrid approaches tackling: scale of datasets needed and deployment; no bottom-up feedback in MSMs (i.e. long time scale social dynamics); less capabilities in behavioral modeling; problems with validation (\textit{rq: I think it is roughly the same for ABMs and CAs, validation standards are rather sparse}). Proposal: space as the bridge between ABM and MSM; GIS as support for ABMs; synthesis of the three. (multi-scale / endogeneity etc. / co-evolution for transport - see \cite{batty2019causality} : many (coupled) models, different perspectives). Behavioral changes linked to policies and reciprocally can better be taken into account.
\end{itemize}

\subsection{Differences between microsimulation and agent-based models}

\textbf{Possible main question for the paper: are ABMs and MSMs so different ?} (what about other models ?)

\subsection{Description of the MOSES model}

%%%%%%%%%%%%
\section{Mapping of the scientific landscape}

\paragraph{Citation network analysis}

\paragraph{Methods}

@@

\subsection{Preliminary results}

@@

\textit{Specificity of community detection in citation networks ? } \cite{chen2010community} directed top-down modularity maximization (citation communities in PR publications) ; \cite{malliaros2013clustering} review of methods for directed modularity detection.

%%%%%%%%%%%
\subsection{Interdisciplinarity levels and bridge publications}

Questions to be answered using centrality indices (test specific measures ? \cite{latora2007measure}) and interdisciplinarity measures \cite{leydesdorff2011indicators}

@@

\textit{Possible meta-analysis ?} $\rightarrow$ collect characteristics for more models; link to disciplinary/semantic characateristics

@@

%%%%%%%%%%%%
\begin{table}
\begin{threeparttable}
	\caption{Main characteristics of QUANT and MOSES models.}\label{tab:comparison}
	\centering
	\begin{tabular}{|c|p{6cm}|p{6cm}|}
	\toprule
	& QUANT & MOSES \\
	\midrule
Time scale & 10 years $^{\ast 1}$ & 30 years \\
Spatial scale & UK & UK \\
Spatial resolution & MSOA & Ward \\
Agent granularity & Aggregated counts & individual level \\
Static/Dynamic & Equilibrium (static) & Dynamic $^{\ast 2}$ \\
Randomness & Deterministic & Monte-Carlo simulations \\
Process: Transportation & 3 modes $^{\ast 3}$ & NA \\
Process: Economic activities & Accessibility-based relocations & NA \\
Process: Demographics & NA & Data-driven $^{\ast 4}$ \\
Process: Migration flows & Accessibility-based relocations & Data-driven \\
\bottomrule
	\end{tabular}
	\begin{tablenotes}
      \small
      \item $^{\ast 1}$ stylized time scale of metropolitan relocations \cite{wegener2004land}
      \item $^{\ast 2}$ model structure is however stationary - this is an important issue for a possible application to 2070
      \item $^{\ast 3}$ discrete choice for transportation mode is not implemented in QUANT \textbf{(?)} 
      \item $^{\ast 4}$ probabilities of basic demographic events (ageing, mortality, fertility, household formation, health, migration) are computed from data
    \end{tablenotes}
	\end{threeparttable}
\end{table}
%%%%%%%%%%%%

@@

\subsection{Microsimulation and agent-based modeling}

\subsubsection{The MATSim model}

 Matsim is an agent-based approach to transportation demand which is activity-based \cite{horni2016multi}. It can simulate agents behavior within the transportation system (traffic flows) and behavioral patterns generating the travel demand. According to \cite{wise2016transportation}, accurate description of transportation remains a point to be explored for agent-based models. A weak coupling of Quant and Matsim would be interesting in that sense, and allow to precisely explore the consequence of transportation scenarios.

\begin{table}
\caption{Characteristics of the MATSim model}
\begin{tabular}{|c|p{6cm}|}
	\toprule
	& MATSim \\
	\midrule
Time scale & 1 day \\
Spatial scale & Any scale (mostly metropolitan area)\\
Spatial resolution & Activities coordinates \\
Agent granularity & Individual level \\
Static/Dynamic & Dynamic Stochastic User Equilibrium \\
Randomness & Stochastic co-evolutionary algorithm (agent level) \\
Process: Transportation & Several modes; microsimulated\\
Process: Economic activities & Exogenous \\
Process: Demographics & NA (agent schedules as input) \\
Process: Migration flows & NA \textbf{check if origins can change} \\
Process: Transportation congestion & Link queuing
\bottomrule
	\end{tabular}
\end{table}

 More generally, the fuzzy boundary between microsimulation and agent-based modeling may be an interesting point to be investigated, both methodologically and theoretically.
